---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lmPlot

<!-- badges: start -->
<!-- badges: end -->

The goal of lmPlot is to fit two variables from a given data frame into a linear model and visualize it.

The function `plot_lm()` takes in two arguments from the provided tibble column variables and creates a graph based on the linear model from the variables. 

## Installation

lmPlot is not yet on CRAN. You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2021/lmPlot")
```
## Example

This is a basic example which shows you how to plot the linear model of two variables: `cyl` - Number of cylinders and `mpg` - Miles/(US) gallon from the `mtcars` data:

```{r example}
library(lmPlot)
plot_lm(mtcars, cyl, mpg, na.rm = T)
```
